Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
Background de openstack modificado

\subsection{OpenStack}
\label{sec:openstack}
One of the most prominent open-source cloud computing platform for both private 
and public clouds is OpenStack. The OpenStack project was announced in 2010 by 
Rackspace and NASA, and currently developed and distributed by the OpenStack
Foundation with the support of more than 150 relevant companies. OpenStack is a 
cloud operating system that provides Infrastructure as a Service (IaaS) able to 
control large pools of compute, storage, and networking resources throughout a 
datacenter, all managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.

>>>>

\subsection{OpenStack}
\label{sec:openstack}

OpenStack is a cloud operating system that provides Infrastructure as a Service (IaaS). 
It is able to control large pools of compute, storage, and networking resources throughout a 
datacenter. All this resources are managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. 
It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.
